Section Three

### 2020-10-04 new2020/sections/sec03.Rmd
show some results

header-includes:
   - \usepackage{cleveref}
   - \usepackage{booktabs}
---

@@

```{r overall_results,echo=FALSE,cache=TRUE,results="asis",dependson="load_results"}
# res_overall <- eta_talk %>%
#    filter(time_until_arrival > 0) %>%
#    summarize(
#       pf_rmse = sqrt(mean(pf_error^2)),
#       pf_mae = mean(abs(pf_error)),
#       pf_mape = mean(abs(pf_error / time_until_arrival)) * 100,
#       pf_cicov = mean(pf_ci) * 100,
#    #   pf_ci_width = mean(pf_upper - pf_lower),
#    #   pf_ci_lower = quantile(pf_upper - pf_lower, 0.025),
#    #   pf_ci_upper = quantile(pf_upper - pf_lower, 0.975),
#       gtfs_rmse = sqrt(mean(gtfs_error^2)),
#       gtfs_mae = mean(abs(gtfs_error)),
#       gtfs_mape = mean(abs(gtfs_error / time_until_arrival)) * 100
#    ) %>%
#    pivot_longer(everything(),
#       names_to = c("model", ".value"),
#       names_pattern = "([a-z]*)_(.*)"
#    ) %>%
#    mutate(
#       model = c("Particle filter", "Schedule-delay")
#    ) %>%
#    rename(
#       " " = "model",
#       "RMSE (s)" = "rmse",
#       "MAE (s)" = "mae",
#       "MAPE (%)" = "mape",
#       "PICP (%)" = "cicov"
#    )

>>>>

header-includes:
   - \usepackage{cleveref}
   - \usepackage{booktabs}
   - \input{../symbols.tex}
---

@@

```{r overall_results,echo=FALSE,cache=TRUE,results="asis",dependson="load_results"}
res_overall <- eta_talk %>%
   filter(time_until_arrival > 0) %>%
   summarize(
      pf_rmse = sqrt(mean(pf_error^2)),
      pf_mae = mean(abs(pf_error)),
      pf_mape = mean(abs(pf_error / time_until_arrival)) * 100,
      pf_cicov = mean(pf_ci) * 100,
   #   pf_ci_width = mean(pf_upper - pf_lower),
   #   pf_ci_lower = quantile(pf_upper - pf_lower, 0.025),
   #   pf_ci_upper = quantile(pf_upper - pf_lower, 0.975),
      gtfs_rmse = sqrt(mean(gtfs_error^2)),
      gtfs_mae = mean(abs(gtfs_error)),
      gtfs_mape = mean(abs(gtfs_error / time_until_arrival)) * 100
   ) %>%
   pivot_longer(everything(),
      names_to = c("model", ".value"),
      names_pattern = "([a-z]*)_(.*)"
   ) %>%
   mutate(
      model = c("Particle filter", "Schedule-delay")
   ) %>%
   rename(
      " " = "model",
      "RMSE (s)" = "rmse",
      "MAE (s)" = "mae",
      "MAPE (%)" = "mape",
      "PICP (%)" = "cicov"
   )
